Data Preparation

### 2021-07-13 x0_data-preparation.Rmd
sort of zooming in on parameters for upper/lower limit in window size: uplim = 0.8, lowlim = 0.2, step = 60

```{r}
# read all files (note adpat function name)
fns <- list_apt_files()

@@

>>>>

loop deactivated as base data has been saved out and shared across the project team

```{r, eval=FALSE}
# read all files (note adpat function name)
fns <- list_apt_files()

@@

```{r}
# comparator levels
uplim  <- .80
lowlim <- .20
slide  <-  60

tmp <- us %>% 
  mutate( N_sm    = roll_quantile(N, width = 7, p = .50)
         ,MED     = roll_quantile(N, width = 14, p = .50, min_obs = 7)
         ,UP_THR  = roll_quantile(N, width = slide, p = uplim,  min_obs = 7)
         ,LOW_THR = roll_quantile(N, width = slide, p = lowlim, min_obs = 7)
         ,LOW_CRIT= LOW_THR >= MED
         ,UP_CRIT = UP_THR  <= MED
         ,STATE   = case_when( !LOW_CRIT & !UP_CRIT ~ "LEVEL"
                              , LOW_CRIT & !UP_CRIT ~ "CRUNCH"
                              ,!LOW_CRIT &  UP_CRIT ~ "RECOV" 
                              ,TRUE ~ "UNKWN")
         ,BAND    = 4000
         ) %>%
  filter(DATE >= lubridate::ymd("2019-10-01"))

tmp %>%
  ggplot() +
  geom_line(aes(x = DATE, y = N), colour = "grey80") +
  geom_line(aes(x = DATE, y = N_sm, colour = THRES2, group = "RQ"), size = 2) +
  geom_line(aes(x = DATE, y = UP_THR), color = "blue") +
  geom_line(aes(x = DATE, y = LOW_THR), color = "red") +
  geom_line(aes(x = DATE, y = MED), color = "green") +
  geom_line(aes(x = DATE, y = BAND, group= "1"), colour = if_else(tmp$LOW_CRIT, "red","green"), size = 4) +
  geom_line(aes(x = DATE, y = BAND-500, group= "1"), colour = if_else(tmp$UP_CRIT, "red","green"), size = 4) +
  geom_line(aes(x = DATE, y = BAND-1500, group= "1", colour = STATE), size = 4) +
  theme_minimal() +
  theme(legend.position = "none")
```
